Treatment_Outcomes

### 2023-04-21 Diagnosis_Vis.Rmd
Added comorbid stuff. Can't figure out CODUS/COXUS post scores.

## Create Diagnosis Variables 
```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
          # Personality Disorders
                #BPD_P is for current BPD
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
            # Somatic Disroders
                    Somatic_D = as.factor(
                      ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
                        1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Stress and Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", 
                      ifelse(Eating_D == 1, "Eating", 
                      ifelse(Somatic_D == 1, "Somatic", NA
                      )))))))))),

          #emotional disorders
                  Emotional_dis = as.factor(
                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
                           Mood_D == 1, "Emotional Disorder", "Other Disorder"))
                  )
 # Comorbid_Anx = as.factor(
                      #   ifelse(Anxiety_D == 1 & Mood_D == 1 |
                      #           Anxiety_D == 1 & OCD_C == 1 |
                      #           Anxiety_D == 1 & BPD_C == 1 |
                      #           Anxiety_D == 1 & Substance_D == 1 |
                      #           Anxiety_D == 1 & Trauma_D == 1 | 
                      #           Anxiety_D == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_Mood = as.factor(
                      #   ifelse(Mood_D == 1 & Anxiety_D == 1 |
                      #           Mood_D == 1 & BPD_C == 1 |
                      #           Mood_D == 1 & BPD_C == 1 |
                      #           Mood_D == 1 & Substance_D == 1 |
                      #           Mood_D == 1 & Trauma_D == 1 | 
                      #           Mood_D == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_OCD = as.factor(
                      #   ifelse(OCD_C == 1 & Anxiety_D == 1 |
                      #           OCD_C == 1 & Mood_D == 1 |
                      #           OCD_C == 1 & BPD_C == 1 |
                      #           OCD_C == 1 & Substance_D == 1 |
                      #           OCD_C == 1 & Trauma_D == 1 | 
                      #           OCD_C == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_BPD = as.factor(
                      #   ifelse(BPD_C == 1 & Anxiety_D == 1 |
                      #           BPD_C == 1 & Mood_D == 1 |
                      #           BPD_C == 1 & OCD_C == 1 |
                      #           BPD_C == 1 & Substance_D == 1 |
                      #           BPD_C == 1 & Trauma_D == 1 | 
                      #           BPD_C == 1 & Eating_D ==1, 1, 0)),

>>>>

## Create Diagnosis Variables 
```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
          # Personality Disorders
                #BPD_P is for current BPD
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
            # Somatic Disroders
                    Somatic_D = as.factor(
                      ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
                        1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Stress and Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", 
                      ifelse(Eating_D == 1, "Eating", 
                      ifelse(Somatic_D == 1, "Somatic", NA
                      )))))))))),
                  Anxiety_C =  as.factor(
                    ifelse(  GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
                        Social_C == 1 | Specific_C == 1, 1, 0)),
                  Mood_C =  as.factor(
                    ifelse(MDD_C ==1 | Bipolar1_C == 1 | Bipolar2_C == 1 | Dysthymia_C == 1, 1, 0)),
                  Substance_C = as.factor(
                    ifelse(Alcohol_C == 1 | Drug_C ==1, 1, 0)),
                  Trauma_C = as.factor(
                    ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
                  Psychotic_C = as.factor(
                    ifelse(Schiz_C == 1 | Schizaff_C == 1,1,0)),
                  Eating_C = as.factor(
                    ifelse(Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),
                  Somatic_C = as.factor(
                    ifelse(Somat_C == 1 | UndiffSoma_C == 1| Hypochondriasis_C ==1, 1,0)),
          #emotional disorders
                  Emotional_dis = as.factor(
                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
                           Mood_D == 1, "Emotional Disorder", "Other Disorder")),
                  Co_Anx = as.factor(
                        ifelse(Anxiety_D == 1 & Mood_C == 1 |
                                Anxiety_D == 1 & OCD_C == 1 |
                                Anxiety_D == 1 & BPD_C == 1 |
                                Anxiety_D == 1 & Substance_C == 1 |
                                Anxiety_D == 1 & Trauma_C == 1 |
                                Anxiety_D == 1 & Eating_C ==1 |
                                Anxiety_D == 1 & Psychotic_C ==1 |
                                Anxiety_D == 1 & Somatic_C ==1, 1, 0)),
                  Co_Mood = as.factor(
                        ifelse(Mood_D == 1 & Anxiety_C == 1 |
                                Mood_D == 1 & OCD_C == 1 |
                                Mood_D == 1 & BPD_C == 1 |
                                Mood_D == 1 & Substance_C == 1 |
                                Mood_D == 1 & Trauma_C == 1 |
                                Mood_D == 1 & Eating_C ==1 |
                                Mood_D == 1 & Psychotic_C ==1 |
                                Mood_D == 1 & Somatic_C ==1 , 1, 0)),
                  Co_OCD = as.factor(
                        ifelse(OCD_C == 1 & Anxiety_C == 1 |
                                OCD_C == 1 & Mood_C == 1 |
                                OCD_C == 1 & BPD_C == 1 |
                                OCD_C == 1 & Substance_C == 1 |
                                OCD_C == 1 & Trauma_C == 1 |
                                OCD_C == 1 & Eating_C ==1 |
                                OCD_C == 1 & Psychotic_C ==1 |
                                OCD_C == 1 & Somatic_C ==1, 1, 0)),
                  CO_BPD = as.factor(
                        ifelse(BPD_C == 1 & Anxiety_C == 1 |
                                BPD_C == 1 & Mood_C == 1 |
                                BPD_C == 1 & OCD_C == 1 |
                                BPD_C == 1 & Substance_C == 1 |
                                BPD_C == 1 & Trauma_C == 1 |
                                BPD_C == 1 & Eating_C ==1 |
                                BPD_C == 1 & Psychotic_C ==1 |
                                BPD_C == 1 & Somatic_C ==1 , 1, 0)),
                  CO_Psychotic = as.factor(
                       ifelse(Psychotic_D == 1 & Mood_C == 1 |
                                Psychotic_D == 1 & OCD_C == 1 |
                                Psychotic_D == 1 & BPD_C == 1 |
                                Psychotic_D == 1 & Substance_C == 1 |
                                Psychotic_D == 1 & Trauma_C == 1 |
                                Psychotic_D == 1 & Eating_C ==1 |
                                Psychotic_D == 1 & Anxiety_C ==1 |
                                Psychotic_D == 1 & Somatic_C ==1, 1, 0)),
                  CO_Eating = as.factor(
                      ifelse(Eating_D == 1 & Mood_C == 1 |
                                Eating_D == 1 & OCD_C == 1 |
                                Eating_D == 1 & BPD_C == 1 |
                                Eating_D == 1 & Substance_C == 1 |
                                Eating_D == 1 & Trauma_C == 1 |
                                Eating_D == 1 & Psychotic_C ==1 |
                                Eating_D == 1 & Anxiety_C ==1 |
                                Eating_D == 1 & Somatic_C ==1, 1, 0)),
                  CO_Somatic =  as.factor(
                       ifelse(Somatic_D == 1 & Mood_C == 1 |
                                Somatic_D == 1 & OCD_C == 1 |
                                Somatic_D == 1 & BPD_C == 1 |
                                Somatic_D == 1 & Substance_C == 1 |
                                Somatic_D == 1 & Trauma_C == 1 |
                                Somatic_D == 1 & Eating_C ==1 |
                                Somatic_D == 1 & Anxiety_C ==1 |
                                Somatic_D == 1 & Psychotic_C ==1, 1, 0)))

### 2023-04-21 Treatment_Outcomes.Rmd
Added comorbid stuff. Can't figure out CODUS/COXUS post scores.

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership_Pre_Post <- Mothership %>%
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

Mothership_Pre_Post$Days_complete_W

@@

#3. Extract the valeues for each patient at their last day (length of stay)
# Mothership_Pre_Post <- mutate(Mothership_Pre_Post,
#             CUDOS_post = CUDOS_post,
#             CUXOS_post = CUXOS_post)
    ##### Why is it not includeing NAs.

CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]

#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost_test
colnames(AnxDep_PrePost)[1] = "ID1"

## This is where I am Figure out where to go from here *******************
#5. Create long dataframe

>>>>

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership <- Mothership %>%
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

Mothership$Days_complete_W

@@

#### Figure out how to:
    #1. write a for /while loop to get a final value. 
    #2. get values for NAs for days attended, 
    #3. get values so this can go into the whole mothership dataset.

#3. Extract the valeues for each patient at their last day (length of stay)
 Mothership <- mutate(Mothership,
            # CUDOS_post = CUDOS_post)
            CUXOS_post = CUXOS_post)
    ##### Why is it not includeing NAs.

CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]

CUDOS_post
Mothership %>%
  mutate(Dep_post = CUDOS_post)

CUDOS_post
#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost_test
colnames(AnxDep_PrePost)[1] = "ID1"

AnxDep_PrePost_test
## This is where I am Figure out where to go from here *******************
#5. Create long dataframe
